The supernova-regulated ISM - III. Magnetic fields in the multi-phase gas

### 2015-03-13 paper.tex

%\boldmath
%-----------------------------------------------------------------------------
\subsection{Field line equation for a vector field, $\bvec{B}(\bvec{x})$}
%-----------------------------------------------------------------------------
%\unboldmath

@@

In Figure \ref{fig:fld_lines}, data from the snapshot at $t=1.4$ Gyr are used. The white field lines have been seeded along the $xz$-axis at $y=-0.51$ kpc. The translucent gas inside the box is a representation of the log density field. Density decreases from brighter to darker colours. Since the warm and hot phase represents approximately $\%99$ of the volume of the ISM gas, it is only useful for visualising the characteristics of the field line within the warm and hot phases.

%-----------------------------------------------------------------------------
\subsection{3D rendering of field lines of the mean magnetic field}
%-----------------------------------------------------------------------------

\begin{figure*}
  \vspace{0cm}
  \centering
\hspace*{0cm} \includegraphics[width=\linewidth]{snapshot1.png}
%\hspace*{0cm} \includegraphics[width=\linewidth]{snapshot1new.png}
\hspace*{0cm} \caption{3D rendering of the field lines of the mean magnetic field. The white lines are field lines seeded along a regular grid on the $xz$-plane at $y\approx-0.5$ kpc. 
  \label{fig:fld_lines}}
  \end{figure*}
\begin{figure}
\centering
\includegraphics[width=\linewidth]{sline_vs_fld1.pdf}
\caption{PDFs of entropy (blue), $s$, log density (red), $\log(n)$, and log temperature (green), $\log(T)$, along field lines (solid) and straight lines (dashed).}
\label{fig:pdfs_mean}
\end{figure}
%-----------------------------------------------------------------------------

>>>>

%\boldmath
%-----------------------------------------------------------------------------
\subsection{Methods for numerical analysis of magnetic field lines}
\subsubsection{Field line equation for a vector field, $\bvec{B}(\bvec{x})$}
%-----------------------------------------------------------------------------
%\unboldmath

@@

In Figure \ref{fig:fld_lines}, data from the snapshot at $t=1.4$ Gyr are used.
The white field lines have been seeded along the $xz$-axis at $y=-0.51$ kpc. 
The translucent gas inside the box is a representation of the log density field.
Density decreases from brighter to darker colours. 
Since the warm and hot phase represents approximately $\%99$ of the volume of the ISM gas, it is only useful for visualising the characteristics of the field line within the warm and hot phases.
